A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-20 doc/large_strain.tex

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work,
however we provide a preliminary weak scaling results that confirm that the matrix-free and multigrid frameworks provided by \texttt{deal.II} library can provide a competitive solution for that case as well.
Table \ref{tab:weak_3d} demonstrates a very good weak scaling up to 1280 processes (64 nodes, the maximum we could request on the local HPC cluster) of the wall time for a single matrix-vector product and a single iteration in the CG solver for the 3D problem with quadratic basis.
}

>>>>

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work,
however we show preliminary weak scaling results that confirm that the matrix-free and multigrid frameworks implemented in the \texttt{deal.II} library can provide a competitive solution for that case as well.
Table \ref{tab:weak_3d} demonstrates a good weak scaling up to 1280 processes (64 nodes, the maximum we could request on the local HPC cluster) of the wall time for a single matrix-vector product and a single iteration in the CG solver for the 3D problem with quadratic basis.
}
